Data Management for LSST Special Programs

### 2023-10-18 sec_intro.tex
rm joinable, leave as detail

\item Special Processing should be done by Rubin Data Management to 
produce unique and separate (but joinable) data products
for Special Programs when it is both possible and necessary.
(Section~\ref{ssec:sci_sproc}).

>>>>

\item Special Processing should be done by Rubin Data Management to 
produce unique and separate data products
for Special Programs when it is both possible and necessary.
(Section~\ref{ssec:sci_sproc}).
